---
title: "Fractional Regression Using Facebook Data"
subtitle: " "
author: Francisco Rowe
output: html_notebook
---

Dependencies
```{r, message=FALSE, warning=FALSE}
 #remotes::install_github(“glmmTMB/glmmTMB/glmmTMB”) 
#install.packages(“viridisLite”) 
#install.packages(“multidplyr”) 
#install.packages(“speedglm”) 
#install.packages(“gpuGlm”)

#data wrangling
library(multidplyr) 
library(tidyverse) 
library(dplyr) 
# estimating mixed effects models 
library(lme4) 
library(merTools) 
library(glmmTMB) 
library(nlme) 
library(speedglm) 
#library(gpuGlm) 
# data visualisation 
library(viridis)
library(viridisLite)
  # reporting regression results
library(broom.mixed)
library(gtsummary)
library(sjPlot)
```



# Data
A cross-section should provide a max set of 6080 * 6079 pairs of origin-destination, including intra-mobility
```{r}
rm(list=ls())
cluster <- new_cluster(12)
df <- readRDS("/Volumes/ITINERANT/pre-processed-movements/movements.rds")
origin <- as.data.frame(unique(df$start_quadkey)) 

destination <- as.data.frame(unique(df$end_quadkey))
```

# Data wrangling
removing mobility counts = na
```{r}
df <- df[complete.cases(df[ , "n_crisis"]), ]
```

removing intra-mobility counts
```{r}
df <- df %>% mutate(
    within = ifelse( start_quadkey == end_quadkey, TRUE, FALSE)
    ) %>%
  filter(within == FALSE)
```

computing proportion of people who moved between tiles
```{r}
df <- df %>% group_by(start_quadkey, end_quadkey, time_interval) %>% 
  partition(cluster) %>% 
  mutate(
  prob_mob = n_crisis / start_FBpop,
  start_cluster = as.factor(start_cluster),
  end_cluster = as.factor(end_cluster)
) %>% 
  collect()
```


```{r}
ggplot(data = dplyr::filter(df, time_interval==2)) +
  geom_histogram(bins = 100, aes(x = prob_mob, y = ..density..)) +
  geom_density(alpha=0.5, aes(x = prob_mob))
```

removing proportions greater than 1
```{r}
#check <- df %>% filter(prob_mob > 1)
df <- df %>% 
  group_by(start_quadkey, end_quadkey, time_interval) %>% 
  partition(cluster) %>% 
  filter(prob_mob <= 1) %>% 
  collect() %>% 
  ungroup()

df$fa_class <-fct_cross(df$start_cluster, df$end_cluster)
df$z_start_pop <- (df$start_pop - mean(df$start_pop)) / sd(df$start_pop)
df$z_end_pop <- (df$end_pop - mean(df$end_pop)) / sd(df$end_pop)
df$z_d <- (df$d - mean(df$d)) / sd(df$d)

```
 
creating two separate data frames
```{r}
df1 <- df %>% 
  filter(time_interval==1) %>% 
  mutate(
  time = as.numeric(ordered(date))
)

df1_origin <- as.data.frame(unique(df1$start_quadkey))
df1_destination <- as.data.frame(unique(df1$end_quadkey))
df1_date <- as.data.frame(unique(df1$date))


df2 <- df %>% 
  filter(time_interval==2) %>% 
  mutate(
  time = as.numeric(ordered(date))
)
df2_origin <- as.data.frame(unique(df2$start_quadkey))
df2_destination <- as.data.frame(unique(df2$end_quadkey))
df2_date <- as.data.frame(unique(df2$date))
```

averaging mobility counts for each time interval
```{r}
ave_df <- df %>% 
  group_by(start_quadkey, end_quadkey, time_interval) %>% 
  partition(cluster) %>% 
  summarise(ave_mobility = mean(n_crisis, na.rm = TRUE)) %>% 
  collect()

ave_origin <- as.data.frame(unique(ave_df$start_quadkey)) 
ave_destination <- as.data.frame(unique(ave_df$end_quadkey))
```

creating two separate data frames
```{r}
ave_df1 <- ave_df %>% 
  filter(time_interval==1)

ave_df2 <- ave_df %>% 
  filter(time_interval==2)
```


# Modelling 

Model 1
```{r}
eq1_1 <- prob_mob ~ z_start_pop + z_end_pop + z_d + fa_class
m1_1 <- glm(eq1_1,
          data = df1,
          family = binomial("logit"),
          weights = start_FBpop)
summary(m1_1)
```

Model 2
```{r}
eq2_1 <- prob_mob ~ z_start_pop + z_end_pop + z_d + fa_class + time + hour + wd
m2_1 <- glm(eq2_1,
          data = df1,
          family = binomial("logit"),
          weights = start_FBpop)
summary(m2_1)
```


Model 3
```{r}
eq3_1 <- prob_mob ~ z_start_pop + z_end_pop + z_d + fa_class + splines::ns(time, 3) + hour + wd
m3_1 <- glm(eq3_1,
          data = df1,
          family = binomial("logit"),
          weights = start_FBpop)
summary(m3_1)
```

```{r}
eq3_2 <- prob_mob ~ z_start_pop + z_end_pop + z_d + fa_class + splines::ns(time, 3) + hour + wd
m3_2 <- glm(eq3_2,
          data = df2,
          family = binomial("logit"),
          weights = start_FBpop)
summary(m3_2)
```

Model 4
```{r}
eq4_1 <- prob_mob ~ start_pop + end_pop + d + time + hour + wd +
( 1 | fa_class)
m4_1 <- glmer(eq4_1,
          data = df1,
          family = binomial("logit"),
          weights = start_FBpop)
summary(m4_1)
```
# Visualising regression outputs
{0: 'Countryside',
1: 'Mixed-use countryside',
2: 'Residential areas with high commuting',
3: 'Highly-served, mixed-use areas'}

## Lockdown                
```{r}
m3_1beta <- as.data.frame(summary(m3_1)$coefficients[5:19, 1])
m3_1beta$fa_class_origin <- as.character(c("Mixed-use countryside", "Residential areas with high commuting", "Highly-served, mixed-use areas", "Countryside", "Mixed-use countryside", "Residential areas with high commuting", "Highly-served, mixed-use areas", "Countryside", "Mixed-use countryside", "Residential areas with high commuting", "Highly-served, mixed-use areas", "Countryside", "Mixed-use countryside", "Residential areas with high commuting", "Highly-served, mixed-use areas"))

m3_1beta$fa_class_destination <- as.character(c("Countryside", "Countryside", "Countryside", "Mixed-use countryside", "Mixed-use countryside", "Mixed-use countryside", "Mixed-use countryside", "Residential areas with high commuting", "Residential areas with high commuting", "Residential areas with high commuting", "Residential areas with high commuting", "Highly-served, mixed-use areas", "Highly-served, mixed-use areas", "Highly-served, mixed-use areas", "Highly-served, mixed-use areas"))

m3_1beta$fa_class_origin <- factor(m3_1beta$fa_class_origin, levels=c("Countryside", "Mixed-use countryside", "Residential areas with high commuting", "Highly-served, mixed-use areas"))

m3_1beta$fa_class_destination <- factor(m3_1beta$fa_class_destination, levels=c("Countryside", "Mixed-use countryside", "Residential areas with high commuting", "Highly-served, mixed-use areas"))

m3_1beta <- m3_1beta %>% 
  rename(betas ="summary(m3_1)$coefficients[5:19, 1]")
```

```{r}
png("/Users/Franciscorowe 1/Dropbox/Francisco/Research/in_progress/itinerant/human-mobility/outputs/modelling/coefficients_lockdown.png",units="in", width=10, height=10, res=300)
p1 <- ggplot(m3_1beta, 
       mapping = aes(x= fa_class_origin, y= fa_class_destination, fill= betas)) +
  geom_tile() +
  scale_fill_viridis(name="Coefficients", option ="plasma", begin = 0, end = 1, direction = 1) +
  theme_minimal() +
  labs(title= paste("Lockdown 1"), x="Origin", y="Destination") +
  theme(
     plot.title = element_text(size=22),
     axis.title=element_text(size=20, face="plain"),
     axis.text.y = element_text(size=15),
     axis.text.x = element_text(size=15, angle = 90))
dev.off()
```

# Freedom
```{r}
m3_2beta <- as.data.frame(summary(m3_2)$coefficients[5:19, 1])
m3_2beta$fa_class_origin <- as.character(c("Mixed-use countryside", "Residential areas with high commuting", "Highly-served, mixed-use areas", "Countryside", "Mixed-use countryside", "Residential areas with high commuting", "Highly-served, mixed-use areas", "Countryside", "Mixed-use countryside", "Residential areas with high commuting", "Highly-served, mixed-use areas", "Countryside", "Mixed-use countryside", "Residential areas with high commuting", "Highly-served, mixed-use areas"))

m3_2beta$fa_class_destination <- as.character(c("Countryside", "Countryside", "Countryside", "Mixed-use countryside", "Mixed-use countryside", "Mixed-use countryside", "Mixed-use countryside", "Residential areas with high commuting", "Residential areas with high commuting", "Residential areas with high commuting", "Residential areas with high commuting", "Highly-served, mixed-use areas", "Highly-served, mixed-use areas", "Highly-served, mixed-use areas", "Highly-served, mixed-use areas"))

m3_2beta$fa_class_origin <- factor(m3_2beta$fa_class_origin, levels=c("Countryside", "Mixed-use countryside", "Residential areas with high commuting", "Highly-served, mixed-use areas"))

m3_2beta$fa_class_destination <- factor(m3_2beta$fa_class_destination, levels=c("Countryside", "Mixed-use countryside", "Residential areas with high commuting", "Highly-served, mixed-use areas"))

m3_2beta <- m3_2beta %>% 
  rename(betas ="summary(m3_2)$coefficients[5:19, 1]")
```


```{r}
png("/Users/Franciscorowe 1/Dropbox/Francisco/Research/in_progress/itinerant/human-mobility/outputs/modelling/coefficients_freedom.png",units="in", width=10, height=10, res=300)
ggplot(m3_2beta, 
       mapping = aes(x= fa_class_origin, y= fa_class_destination, fill= betas)) +
  geom_tile() +
  scale_fill_viridis(name="Coefficients", option ="plasma", begin = 0, end = 1, direction = 1) +
  theme_minimal() +
  labs(title= paste("Post Freedom Day"), x="Origin", y="Destination") +
  theme(
     plot.title = element_text(size=22),
     axis.title=element_text(size=20, face="plain"),
     axis.text.y = element_text(size=15),
     axis.text.x = element_text(size=15, angle = 90))
dev.off()
```


## Difference
```{r}
m3_2beta$diff <- m3_2beta$betas - m3_1beta$betas

png("/Users/Franciscorowe 1/Dropbox/Francisco/Research/in_progress/itinerant/human-mobility/outputs/modelling/coefficients_difference.png",units="in", width=10, height=10, res=300)
ggplot(m3_2beta, 
       mapping = aes(x= fa_class_origin, y= fa_class_destination, fill= diff)) +
  geom_tile() +
  scale_fill_viridis(name="Coefficients", option ="plasma", begin = 0, end = 1, direction = 1) +
  theme_minimal() +
  labs(title= paste("Difference"), x="Origin", y="Destination") +
  theme(
     plot.title = element_text(size=22),
     axis.title=element_text(size=20, face="plain"),
     axis.text.y = element_text(size=15),
     axis.text.x = element_text(size=15, angle = 90))
dev.off()
```

