---
title: "Regression Modelling Using Facebook Data"
subtitle: " "
author: Francisco Rowe & Alessia Calafiore
output: html_notebook
---

  Dependencies
```{r, message=FALSE, warning=FALSE}
#data wrangling
#library(multidplyr) 
library(tidyverse) 
library(lubridate)
library(dplyr) 
#diagnostics
library(AER)
# data visualisation 
library(viridis)
library(viridisLite)
library(ggthemes)
library(ggpubr)
# reporting regression results
library(broom)
library(broom.mixed)
library(gtsummary)
library(sjPlot)
library(xtable)
```


## Data
A cross-section should provide a max set of 6080 * 6079 pairs of origin-destination, including intra-mobility
```{r}
rm(list=ls())

df <- readRDS("~/Projects/ITINERANT/full_period_mov_pop.rds") %>% 
  select( -c(tile_size, start_polygon_id, end_polygon_id, country, level, is_statistically_significant, start_quadkey, end_quadkey, n_baseline, n_difference, percent_change, start_lat, start_lon, end_lat, end_lon, geometry) )

# id for unique tiles
origin <- as.data.frame(unique(df$start_polygon_name)) 
destination <- as.data.frame(unique(df$end_polygon_name))

str(df)
```
## Timeline
```{r}

timeline<-data_frame(start=c("2020-03-23","2020-06-01","2020-10-14","2021-01-06","2021-03-29"),end=c("2020-06-01","2020-10-14","2021-01-06","2021-03-29","2021-08-01"),name=c("1-First lockdown","2-Partial re-opening","3-Tier system &\nSecond lockdown","4-Third lockdown","5-Full re-opening"),x=c("2020-04-30","2020-08-01","2020-11-25","2021-02-15","2021-05-30"),y=c(45,45,45,45,45),period=c("1","2","3","4","5"))

timeline<-timeline %>%
  mutate(name=factor(name,levels = c("1-First lockdown","2-Partial re-opening","3-Tier system &\nSecond lockdown","4-Third lockdown","5-Full re-opening")))
  
```
## Visualise timeline and Stringency index

```{r}
stringency_index <- read_csv("~/Projects/human-mobility/stringency_index.csv")
stringency_index$Day<-ymd(as.Date(stringency_index$Day,format = "%d/%m/%y"))

g<-ggplot()+
  geom_rect(
    aes(xmin = as.Date(start), xmax = as.Date(end), fill = name), 
    ymin = -Inf, ymax = Inf, alpha = 0.6, 
    data = timeline
  )+
  geom_line(data = stringency_index, aes(x=Day,y=stringency_index),size = 1)+
  geom_text(data = timeline, aes(x=as.Date(x),y=y,label=period,family="Times New Roman",fontface="bold"),size=16)+
  scale_x_date(date_labels = "%b",
               date_breaks = "1 months", #breaks = c("Mar", "Jun", "Sep", "Dec"),
               limits = c(as.Date("2020-03-01"), as.Date("2021-08-01"))
  )+
  theme_minimal()+
  theme(axis.title.x = element_blank(),
        text=element_text(size=22,family="Times New Roman"),legend.spacing = unit(2.5, 'in'),panel.grid.minor = element_blank(),panel.grid.major.x = element_blank())+
  scale_fill_manual(values = c("#D091BB","#E7F7D5","#D091BB","#B3589A","#9BBF85"))+
  labs(fill="Timeline",y="Stringency Index")

png("~/stringency.png",units="in", width=15, height=5, res=300)
g
dev.off()


  
```


## Data Wrangling

Proportion of people moving
```{r}
df <- df %>% mutate(
  mov_prop = n_crisis / start_pop
) %>% 
  filter(mov_prop <= 1)

```

Creating area class interaction variable
```{r}
df <-  df %>% mutate(
  origin_class = ordered(origin_class, 
                         levels = c("1","2","3","4","5","6","7","8","9","10")),
  destination_class = ordered(destination_class, 
                              levels = c("1","2","3","4","5","6","7","8","9","10")),
  wd = factor(wd,
              levels = c("Weekday", "Weekend"))
)

df$origin_destination_class <- fct_cross(df$origin_class, df$destination_class)
df$day <- as.numeric(ordered(df$date))
df$month <- lubridate::month(lubridate::ymd(df$date), label=TRUE)
month <- unique(df$month)
df$monthyear = lubridate::floor_date(df$date, "month")
monthyear <- unique(df$monthyear)
```

Standardising covariates
```{r}
df$z_origin_pop <- (df$origin_res_pop - mean(df$origin_res_pop)) / sd(df$origin_res_pop)
df$z_destination_pop <- (df$destination_res_pop - mean(df$destination_res_pop)) / sd(df$destination_res_pop)
df$z_d <- (df$length_km - mean(df$length_km)) / sd(df$length_km)
```

Create df with averaged covariates
```{r}
ave_pre_df <- with(df, data.frame(
  origin_destination_class = unique(df$origin_destination_class),
  z_d = mean(z_d),
  z_origin_pop = mean(z_origin_pop),
  z_destination_pop = mean(z_destination_pop),
  day = median(day),
  hour = factor(" 08", levels = c(" 00"," 08", " 16")),
  wd = factor("Weekday", levels = c("Weekday","Weekend")),
  z_score = 2))

```
## Create monthly input
```{r}
for (i in 1:18){
  print(monthyear[i])
  dft<-df[df$monthyear==monthyear[i],]
  saveRDS(dft,paste0("~/Projects/ITINERANT/modelling_input/i_",i,".rds"))
}
```

## Running poisson model with embedded parallelisation and save results
```{r}

for (i in 1:18){
  #print(monthyear[i])
  dft<-readRDS(paste0("~/Projects/ITINERANT/modelling_input/i_",i,".rds"))
  #dft<-df[df$monthyear==monthyear[i],]
  print(summary(dft$month))
  m<-glm(n_crisis ~ z_d + origin_destination_class + z_origin_pop + z_destination_pop + day + hour + wd + z_score, data = dft, family = poisson(link="log"))#, weights = start_pop
  filename<-paste0("~/Projects/ITINERANT/modelling_output/v2_nw/m_",i,".rds")
  saveRDS(m,filename)
  remove(dft,m)
  gc()
  print(i)
}

```

## Extract Coefficients

```{r}
coefficients<-NULL
for (i in 1:18){
  filename<-paste0("~/Projects/ITINERANT/modelling_output/v2/m_",i,".rds")
  m<-readRDS(filename)
  # extracting coefficients
  coefficients_df <- as.data.frame(coefficients(m)) %>%
    rename(estimate =`coefficients(m)`)%>%
    mutate(
      origin_destination_class=rownames(.),
      monthyear=monthyear[i]
    )
  rownames(coefficients_df)<-seq(1:nrow(coefficients_df))
  
  # extracting standard errors
  se_df <- as.data.frame(summary(m)$coefficients[, 2]) %>%
    rename(std_error =`summary(m)$coefficients[, 2]`)%>%
    mutate(
      origin_destination_class=rownames(.),
      monthyear=monthyear[i]
    )
  rownames(se_df)<-seq(1:nrow(se_df))
  
  coefficients_t<-coefficients_df %>%
    inner_join(se_df, by=c("origin_destination_class"="origin_destination_class","monthyear"="monthyear")) %>%
    mutate(
     ci_lower = estimate - ( 1.96 * std_error ),
     ci_upper = estimate + ( 1.96 * std_error )
     )
    
 coefficients<-rbind(coefficients, coefficients_t) 
 print(i)
}

```
## Extract Diagnostics
```{r}

#standard goodness of fit stats: residual deviance, chi-square test, Akaike, Pseudo-R2
#standard overall stats: number of observations, df, log-likelihood
diagnostics<-NULL
for (i in 1:18){
  filename<-paste0("~/Projects/ITINERANT/modelling_output/v2/m_",i,".rds")
   m<-readRDS(filename)
   month<-m$data[1,]$monthyear
   residual_deviance<-m$deviance
   #p_chi_test<-pchisq(m$deviance, df = m$df.residual, lower.tail=FALSE) #P[X > x]
   Akaike<-AIC(m)
   pseudo_r<-round(1-(m$deviance/m$null.deviance),3)
   n_obs<-nrow(m$data)
   df<-df.residual(m)
   logLik<-as.data.frame(logLik(m))$`c(x)`
   d<-data.frame(month,residual_deviance,Akaike,pseudo_r,n_obs,df,logLik)
   diagnostics<-rbind(diagnostics,d)
   print(i)
}   


diagnostics %>%
  mutate(month=format_ISO8601(diagnostics$month, precision = "ym"))%>%
  kbl(caption="Poisson Regression Monthly Models Diagnostics.",
       format= "latex",
   col.names = c("Month-Year","Residual Deviance","Akaike","Pseudo R squared","Number of Obs.","Degrees of Freedom","Log-Likelihood"),
                  align="r") %>%
   kable_classic(full_width = F, html_font = "times new roman")


library(AER)
for (i in 1:18){
  filename<-paste0("~/Projects/ITINERANT/modelling_output/v2_nw/m_",i,".rds")
   m<-readRDS(filename)
   print(monthyear[i])
   print(dispersiontest(m,trafo = 1))#
}
```


## Visualising other co-variates coefficients

```{r}

coefficients_NOD<-coefficients %>%
  filter(!grepl("origin_destination",origin_destination_class))


###intercept
data=coefficients_NOD[coefficients_NOD$origin_destination_class=="(Intercept)",]

g<-ggplot()+
   geom_rect(
    aes(xmin = as.Date(start), xmax = as.Date(end), fill = name), 
    ymin = -Inf, ymax = Inf, alpha = 0.6, 
    data = timeline
  ) +
   geom_line(data = data, aes(x=monthyear,y=estimate),size = 1)+
 geom_ribbon(data = data, aes(x=monthyear, ymin=(ci_lower), ymax=(ci_upper)), alpha=0.35, fill="gray36") +
  scale_x_date(date_labels = "%b",
               date_breaks = "1 months", #breaks = c("Mar", "Jun", "Sep", "Dec"),
               limits = c(as.Date("2020-03-01"), as.Date("2021-08-01"))
  )+
  theme_minimal()+
  theme(axis.title.x = element_blank(),
        text=element_text(size=22,family="Times New Roman"), 
        legend.spacing = unit(2.5, 'in'))+
  scale_fill_manual(values = c("#D091BB","#E7F7D5","#D091BB","#B3589A","#9BBF85"))+
  labs(fill="Timeline",y="Coefficient") 

png("~/intercept.png",units="in", width=15, height=5, res=300)
g
dev.off()

data<-coefficients_NOD[!(coefficients_NOD$origin_destination_class=="(Intercept)"),]
data<-data %>%
  mutate(
    component=case_when(
      origin_destination_class=="day"~"Time",
      origin_destination_class=="hour 08"~"Time",
      origin_destination_class=="hour 16"~"Time",
      origin_destination_class=="wdWeekend"~"Time",
      origin_destination_class=="z_d"~"Distance",
      origin_destination_class=="z_origin_pop"~"OD Population",
      origin_destination_class=="z_destination_pop"~"OD Population",
      origin_destination_class=="z_score"~"Quality Score"
    )
  )
g<-ggplot()+
  geom_rect(
   aes(xmin = as.Date(start), xmax = as.Date(end), fill = name),
   ymin = -Inf, ymax = Inf, alpha = 0.3,
   data = timeline
  ) +
  scale_fill_manual(values = c("#D091BB","#E7F7D5","#D091BB","#B3589A","#9BBF85"))+
  geom_line(data = data,
            aes(x=monthyear,y=estimate,group=origin_destination_class,colour=component),
            size = 1) + 
    geom_ribbon(data = data,
                aes(x=monthyear,ymin=(ci_lower), ymax=(ci_upper),group=origin_destination_class),
                alpha=0.35) +
  scale_color_viridis_d(begin=0,end=1,option = "C")+
  scale_x_date(date_labels = "%b",
               date_breaks = "1 months", #breaks = c("Mar", "Jun", "Sep", "Dec"),
               limits = c(as.Date("2020-03-01"), as.Date("2021-08-01"))
  )+
  theme_minimal()+
  labs(y="Regression Coefficients",color="Covariates Components",fill="Timeline")+
  theme(axis.title.x = element_blank(),text = element_text(size=18,family = "Times New Roman"),panel.grid.major = element_blank(),panel.grid.minor = element_blank())

png("~/glm-nod_coefficients.png",units="in", width=15, height=10, res=300)
g
dev.off()

###create coefficients table

esd<-paste(round(data$estimate,3), " (",round(data$std_error,6),")",sep = "")

rn <-unique(data$monthyear)
rn=format_ISO8601(rn, precision = "ym")

cn<-unique(data$origin_destination_class)

tab <- matrix(esd,18,8,dimnames=list(rn,cn))

xtable(tab)
```

## Visualising OD Coefficients

```{r}
coefficients_OD<-coefficients %>%
  filter(grepl("origin_destination",origin_destination_class))
coefficients_OD<-coefficients_OD %>%
  mutate(
    origin_destination_class=gsub("origin_destination_class","",coefficients_OD$origin_destination_class)
  )%>%
  separate(origin_destination_class, c("origin_class","destination_class"), sep = "([:])") %>%
  mutate(
    origin_destination_class=paste0(origin_class,"_",destination_class),
    origin_class = ordered(origin_class, 
                           levels = c("1","2","3","4","5","6","7","8","9","10")),
    destination_class = ordered(destination_class, 
                                levels = c("1","2","3","4","5","6","7","8","9","10")
    ))


#make plots
g <- ggplot() +
  geom_ribbon(data=coefficients_OD,
             aes(x = monthyear, ymin=(ci_lower), ymax=(ci_upper)),
             alpha=1,
             fill="gray36",
             size=5) +
  geom_rect(
    aes(xmin = as.Date(start), xmax = as.Date(end), fill = name), 
    ymin = -Inf, ymax = Inf, alpha = 0.4, 
    data = timeline
  )+
  geom_line(data = coefficients_OD, 
            aes(x = monthyear, y = estimate), 
            colour = "darkblue",
            size = 1) + 
  facet_grid(origin_class ~ destination_class) +
  theme_tufte() +
  #theme(text = element_text(family="robotocondensed")) +
  theme(legend.position = "bottom",
        text=element_text(size=12),
        plot.subtitle = element_text(color = c('black'), hjust = 0.5, size = 12,face = "bold"),
        axis.text=element_text(size=8),
        axis.text.x=element_text(angle=45),
        axis.title=element_text(size=12),
        axis.title.x = element_blank(),
        legend.text = element_text(size=14),
        legend.box = "vertical"
  ) +
  labs(x= "Month",
       y = "Regression Coefficients",
       subtitle = "Destination Class") +
  scale_x_date(date_labels = "%b",
               date_breaks = "3 months", #breaks = c("Mar", "Jun", "Sep", "Dec"),
               limits = c(as.Date("2020-01-01"), as.Date("2021-08-01"))
  )+
  scale_fill_manual(values = c("#D091BB","#E7F7D5","#D091BB","#B3589A","#9BBF85"))+
  #scale_color_manual(values = c("darkblue","red"),labels=c("OD coef","Intercept"))+
  labs(fill="Timeline")

png("~/glm-coeff-NI.png",units="in", width=13, height=10, res=300)
annotate_figure(g, 
                left = text_grob("Origin Class", 
                                 face= "bold", 
                                 color = "black", 
                                 rot = 90, 
                                 size = 12,
                                 family = "serif"))
dev.off()

###detailed OD for analysis purposes
coefficients_OD_temp<-coefficients_OD %>%
  filter(origin_class %in% c(1, 2, 3, 4, 5) & destination_class %in% c(1, 2, 3, 4, 5))
g <- ggplot() +
  geom_rect(
    aes(xmin = as.Date(start), xmax = as.Date(end), fill = name),
    ymin = -Inf, ymax = Inf, alpha = 0.4,
    data = timeline
  )+
  geom_line(data = coefficients_OD_temp, 
            aes(x = monthyear, y = estimate),
            colour = "dark blue",
            size = 1) + 
  geom_ribbon(data=coefficients_OD_temp, 
              aes(x = monthyear, ymin=(ci_lower), ymax=(ci_upper)), 
              alpha=0.35, 
              fill="gray36") +
  facet_grid(origin_class ~ destination_class) +
  theme(legend.position = "bottom",
        text=element_text(size=12),
        plot.subtitle = element_text(color = c('black'), hjust = 0.5, size = 12,face = "bold"),
        axis.text=element_text(size=8),
        axis.text.x=element_text(angle=45),
        axis.title=element_text(size=12),
        axis.title.x = element_blank(),
        legend.text = element_text(size=14),
        legend.box = "vertical"
  ) +
  labs(x= "Month",
       y = "Regression Coefficients",
       subtitle = "Destination Class") +
  scale_x_date(date_labels = "%b",
               date_breaks = "2 months", #breaks = c("Mar", "Jun", "Sep", "Dec"),
               limits = c(as.Date("2020-03-01"), as.Date("2021-08-01"))
  )+
  scale_fill_manual(values = c("#D091BB","#E7F7D5","#D091BB","#B3589A","#9BBF85"))+
  #scale_color_manual(values = c("darkblue","red"),labels=c("OD coef","Intercept"))+
  labs(fill="Timeline")

png("~/glm-coeff-o1-5-d1-5.png",units="in", width=13, height=10, res=300)
annotate_figure(g, 
                left = text_grob("Origin Class", 
                                 face= "bold", 
                                 color = "black", 
                                 rot = 90, 
                                 size = 12,
                                 family = "serif"))
dev.off()

coefficients_OD_temp<-coefficients_OD %>%
  filter(origin_class %in% c(1, 2, 3, 4, 5) & destination_class %in% c(6, 7, 8, 9, 10))
g <- ggplot() +
  geom_rect(
    aes(xmin = as.Date(start), xmax = as.Date(end), fill = name),
    ymin = -Inf, ymax = Inf, alpha = 0.4,
    data = timeline
  )+
  geom_line(data = coefficients_OD_temp, 
            aes(x = monthyear, y = estimate),
            colour = "dark blue",
            size = 1) + 
  geom_ribbon(data=coefficients_OD_temp, 
              aes(x = monthyear, ymin=(ci_lower), ymax=(ci_upper)), 
              alpha=0.35, 
              fill="gray36") +
  facet_grid(origin_class ~ destination_class) +
  theme(legend.position = "bottom",
        text=element_text(size=12),
        plot.subtitle = element_text(color = c('black'), hjust = 0.5, size = 12,face = "bold"),
        axis.text=element_text(size=8),
        axis.text.x=element_text(angle=45),
        axis.title=element_text(size=12),
        axis.title.x = element_blank(),
        legend.text = element_text(size=14),
        legend.box = "vertical"
  ) +
  labs(x= "Month",
       y = "Regression Coefficients",
       subtitle = "Destination Class") +
  scale_x_date(date_labels = "%b",
               date_breaks = "2 months", #breaks = c("Mar", "Jun", "Sep", "Dec"),
               limits = c(as.Date("2020-03-01"), as.Date("2021-08-01"))
  )+
  scale_fill_manual(values = c("#D091BB","#E7F7D5","#D091BB","#B3589A","#9BBF85"))+
  labs(fill="Timeline")

png("~/glm-coeff-o1-5-d6-10.png",units="in", width=13, height=10, res=300)
annotate_figure(g, 
                left = text_grob("Origin Class", 
                                 face= "bold", 
                                 color = "black", 
                                 rot = 90, 
                                 size = 12,
                                 family = "serif"))
dev.off()

coefficients_OD_temp<-coefficients_OD %>%
  filter(origin_class %in% c(6, 7, 8, 9, 10) & destination_class %in% c(1, 2, 3, 4, 5))
g <- ggplot() +
  geom_rect(
    aes(xmin = as.Date(start), xmax = as.Date(end), fill = name),
    ymin = -Inf, ymax = Inf, alpha = 0.4,
    data = timeline
  )+
  geom_line(data = coefficients_OD_temp, 
            aes(x = monthyear, y = estimate),
            colour = "dark blue",
            size = 1) + 
  geom_ribbon(data=coefficients_OD_temp, 
              aes(x = monthyear, ymin=(ci_lower), ymax=(ci_upper)), 
              alpha=0.35, 
              fill="gray36") +
  facet_grid(origin_class ~ destination_class) +
  theme(legend.position = "bottom",
        text=element_text(size=12),
        plot.subtitle = element_text(color = c('black'), hjust = 0.5, size = 12,face = "bold"),
        axis.text=element_text(size=8),
        axis.text.x=element_text(angle=45),
        axis.title=element_text(size=12),
        axis.title.x = element_blank(),
        legend.text = element_text(size=14),
        legend.box = "vertical"
  ) +
  labs(x= "Month",
       y = "Regression Coefficients",
       subtitle = "Destination Class") +
  scale_x_date(date_labels = "%b",
               date_breaks = "2 months", #breaks = c("Mar", "Jun", "Sep", "Dec"),
               limits = c(as.Date("2020-03-01"), as.Date("2021-08-01"))
  )+
  scale_fill_manual(values = c("#D091BB","#E7F7D5","#D091BB","#B3589A","#9BBF85"))+
  labs(fill="Timeline")

png("~/glm-coeff-o6-10-d1-5.png",units="in", width=13, height=10, res=300)
annotate_figure(g, 
                left = text_grob("Origin Class", 
                                 face= "bold", 
                                 color = "black", 
                                 rot = 90, 
                                 size = 12,
                                 family = "serif"))
dev.off()

coefficients_OD_temp<-coefficients_OD %>%
  filter(origin_class %in% c(6, 7, 8, 9, 10) & destination_class %in% c(6, 7, 8, 9, 10))
g <- ggplot() +
  geom_rect(
    aes(xmin = as.Date(start), xmax = as.Date(end), fill = name),
    ymin = -Inf, ymax = Inf, alpha = 0.4,
    data = timeline
  )+
  geom_line(data = coefficients_OD_temp, 
            aes(x = monthyear, y = estimate),
            colour = "dark blue",
            size = 1) + 
  geom_ribbon(data=coefficients_OD_temp, 
              aes(x = monthyear, ymin=(ci_lower), ymax=(ci_upper)), 
              alpha=0.35, 
              fill="gray36") +
  facet_grid(origin_class ~ destination_class) +
  theme(legend.position = "bottom",
        text=element_text(size=12),
        plot.subtitle = element_text(color = c('black'), hjust = 0.5, size = 12,face = "bold"),
        axis.text=element_text(size=8),
        axis.text.x=element_text(angle=45),
        axis.title=element_text(size=12),
        axis.title.x = element_blank(),
        legend.text = element_text(size=14),
        legend.box = "vertical"
  ) +
  labs(x= "Month",
       y = "Regression Coefficients",
       subtitle = "Destination Class") +
  scale_x_date(date_labels = "%b",
               date_breaks = "2 months", #breaks = c("Mar", "Jun", "Sep", "Dec"),
               limits = c(as.Date("2020-03-01"), as.Date("2021-08-01"))
  )+
  scale_fill_manual(values = c("#D091BB","#E7F7D5","#D091BB","#B3589A","#9BBF85"))+
  labs(fill="Timeline")

png("~/glm-coeff-o6-10-d6-10.png",units="in", width=13, height=10, res=300)
annotate_figure(g, 
                left = text_grob("Origin Class", 
                                 face= "bold", 
                                 color = "black", 
                                 rot = 90, 
                                 size = 12,
                                 family = "serif"))
dev.off()

```

## Getting Predictions

```{r}

pred_prob<-NULL
for (i in 1:18){
  ave_pre_df_temp<-ave_pre_df
  filename<-paste0("~/Projects/ITINERANT/modelling_output/v2/m_",i,".rds")
  m<-readRDS(filename)
  predict<-predict.glm(m, newdata = ave_pre_df, "response", se.fit = TRUE)
  ave_pre_df_temp<- ave_pre_df_temp %>%
    mutate(
      probs=predict$fit,
      std_error=predict$se.fit,
      ci_lower = probs - ( 1.96 * std_error ) ,
      ci_upper = probs + ( 1.96 * std_error ),
      monthyear=monthyear[i]
    )
  
  pred_prob<-rbind(pred_prob,ave_pre_df_temp[c("origin_destination_class","probs","ci_lower","ci_upper","monthyear")])
  print(i)
}
```

## Visualising predictions

```{r}
#data prep
pred_prob<-pred_prob %>%
  separate(origin_destination_class, c("origin_class","destination_class"), sep = "([:])") %>%
  mutate(
    origin_destination_class=paste0(origin_class,"_",destination_class),
    origin_class = ordered(origin_class, 
                           levels = c("1","2","3","4","5","6","7","8","9","10")),
    destination_class = ordered(destination_class, 
                                levels = c("1","2","3","4","5","6","7","8","9","10")
    ))

#make plots
g <- ggplot() +
  geom_rect(
    aes(xmin = as.Date(start), xmax = as.Date(end), fill = name), 
    ymin = -Inf, ymax = Inf, alpha = 0.4, 
    data = timeline
  )+
  geom_line(data = pred_prob, 
            aes(x = monthyear, y = probs), 
            size = 1,
            color="dark blue") + 
  geom_ribbon(data=coefficients_OD, 
              aes(x = monthyear, ymin=(ci_lower), ymax=(ci_upper)), 
              alpha=0.35, 
              fill="gray36") +
  #facet_wrap(~ origin_destination_class, nrow = 10) +
  facet_grid(origin_class ~ destination_class) +
  theme_tufte() +
  #theme(text = element_text(family="robotocondensed")) +
  theme(legend.position = "bottom",
        text=element_text(size=12),
        plot.subtitle = element_text(color = c('black'), hjust = 0.5, size = 12,face = "bold"),
        axis.text=element_text(size=8),
        axis.text.x=element_text(angle=45),
        axis.title=element_text(size=12),
        axis.title.x = element_blank(),
        legend.text = element_text(size=14)
  ) +
  labs(x= "Month",
       y = "Regression Predictions",
       subtitle = "Destination Class") +
  scale_x_date(date_labels = "%b",
               date_breaks = "3 months", #breaks = c("Mar", "Jun", "Sep", "Dec"),
               limits = c(as.Date("2020-01-01"), as.Date("2021-08-01"))
  )+
  scale_fill_manual(values = c("#D091BB","#E7F7D5","#D091BB","#B3589A","#9BBF85"))+
  labs(fill="Timeline")

png("~/glm-probs.png",units="in", width=13, height=10, res=300)
annotate_figure(g, 
                left = text_grob("Origin Class", 
                                 face= "bold", 
                                 color = "black", 
                                 rot = 90, 
                                 size = 12,
                                 family = "serif"))
dev.off()

#detailed plot for analysis purposes
g1 <- pred_prob %>% 
  filter(origin_class %in% c(1, 2, 3, 4, 5) & destination_class %in% c(1, 2, 3, 4, 5)) %>%
  ggplot(., aes(x = monthyear, y = probs, group = origin_destination_class)) +
  geom_hline( yintercept = 0, linetype = "solid", colour = "gray85", size = 0.5) +
  geom_vline( xintercept = as.numeric(as.Date("2020-03-23")), linetype = "solid", colour = "gray85", size = 0.2) +
  geom_vline( xintercept = as.numeric(as.Date("2021-03-08")), linetype = "solid", colour = "gray85", size = 0.2) +
  geom_vline( xintercept = as.numeric(as.Date("2021-04-12")), linetype = "solid", colour = "gray85", size = 0.2) +
  geom_vline( xintercept = as.numeric(as.Date("2021-07-19")), linetype = "solid", colour = "gray85", size = 0.2) +
  geom_line(colour = "darkblue", size = 1) + 
  geom_ribbon(aes(ymin=(ci_lower), ymax=(ci_upper)), alpha=0.35, fill="gray36") +
  #facet_wrap(~ coefficient, nrow = 10) +
  facet_grid(origin_class ~ destination_class) +
  theme_tufte() +
  #theme(text = element_text(family="robotocondensed")) +
  theme(legend.position = "none",
        text=element_text(size=12),
        plot.subtitle = element_text(color = c('black'), hjust = 0.5, size = 12,face = "bold"),
        axis.text=element_text(size=8),
        axis.title=element_text(size=12)
  ) +
  labs(x= "Month",
       y = "Regression Probs",
       subtitle = "Destination Class") +
  scale_x_date(date_labels = "%b",
               date_breaks = "3 months", #breaks = c("Mar", "Jun", "Sep", "Dec"),
               limits = c(as.Date("2020-01-01"), as.Date("2021-08-01"))
  )

png("~/glm-probs_class_o1-5_d1-5.png",units="in", width=10, height=10, res=300)
annotate_figure(g1, 
                left = text_grob("Origin Class", 
                                 face= "bold", 
                                 color = "black", 
                                 rot = 90, 
                                 size = 12,
                                 family = "serif"))
dev.off()

g2 <- pred_prob %>% 
  filter(origin_class %in% c(1, 2, 3, 4, 5) & destination_class %in% c(6, 7, 8, 9, 10)) %>%
  ggplot(., aes(x = monthyear, y = probs, group = origin_destination_class)) +
  geom_hline( yintercept = 0, linetype = "solid", colour = "gray85", size = 0.5) +
  geom_vline( xintercept = as.numeric(as.Date("2020-03-23")), linetype = "solid", colour = "gray85", size = 0.2) +
  geom_vline( xintercept = as.numeric(as.Date("2021-03-08")), linetype = "solid", colour = "gray85", size = 0.2) +
  geom_vline( xintercept = as.numeric(as.Date("2021-04-12")), linetype = "solid", colour = "gray85", size = 0.2) +
  geom_vline( xintercept = as.numeric(as.Date("2021-07-19")), linetype = "solid", colour = "gray85", size = 0.2) +
  geom_line(colour = "darkblue", size = 1) + 
  geom_ribbon(aes(ymin=(ci_lower), ymax=(ci_upper)), alpha=0.35, fill="gray36") +
  facet_grid(origin_class ~ destination_class) +
  theme_tufte() +
  #theme(text = element_text(family="robotocondensed")) +
  theme(legend.position = "none",
        text=element_text(size=12),
        plot.subtitle = element_text(color = c('black'), hjust = 0.5, size = 12,face = "bold"),
        axis.text=element_text(size=8),
        axis.title=element_text(size=12)
  ) +
  labs(x= "Month",
       y = "Regression Probs",
       subtitle = "Destination Class") +
  scale_x_date(date_labels = "%b",
               date_breaks = "3 months", #breaks = c("Mar", "Jun", "Sep", "Dec"),
               limits = c(as.Date("2020-01-01"), as.Date("2021-08-01"))
  )

png("~/glm-probs_class_o1-5_d6-10.png",units="in", width=10, height=10, res=300)
annotate_figure(g2, 
                left = text_grob("Origin Class", 
                                 face= "bold", 
                                 color = "black", 
                                 rot = 90, 
                                 size = 12,
                                 family = "serif"))
dev.off()


g3 <- pred_prob %>% 
  filter(origin_class %in% c(6, 7, 8, 9, 10) & destination_class %in% c(1, 2, 3, 4, 5)) %>%
  ggplot(., aes(x = monthyear, y = probs, group = origin_destination_class)) +
  geom_hline( yintercept = 0, linetype = "solid", colour = "gray85", size = 0.5) +
  geom_vline( xintercept = as.numeric(as.Date("2020-03-23")), linetype = "solid", colour = "gray85", size = 0.2) +
  geom_vline( xintercept = as.numeric(as.Date("2021-03-08")), linetype = "solid", colour = "gray85", size = 0.2) +
  geom_vline( xintercept = as.numeric(as.Date("2021-04-12")), linetype = "solid", colour = "gray85", size = 0.2) +
  geom_vline( xintercept = as.numeric(as.Date("2021-07-19")), linetype = "solid", colour = "gray85", size = 0.2) +
  geom_line(colour = "darkblue", size = 1) + 
  geom_ribbon(aes(ymin=(ci_lower), ymax=(ci_upper)), alpha=0.35, fill="gray36") +
  facet_grid(origin_class ~ destination_class) +
  theme_tufte() +
  #theme(text = element_text(family="robotocondensed")) +
  theme(legend.position = "none",
        text=element_text(size=12),
        plot.subtitle = element_text(color = c('black'), hjust = 0.5, size = 12,face = "bold"),
        axis.text=element_text(size=8),
        axis.title=element_text(size=12)
  ) +
  labs(x= "Month",
       y = "Regression Probs",
       subtitle = "Destination Class") +
  scale_x_date(date_labels = "%b",
               date_breaks = "3 months", #breaks = c("Mar", "Jun", "Sep", "Dec"),
               limits = c(as.Date("2020-01-01"), as.Date("2021-08-01"))
  )

png("~/glm-probs_class_o6-10_d1-5.png",units="in", width=10, height=10, res=300)
annotate_figure(g3, 
                left = text_grob("Origin Class", 
                                 face= "bold", 
                                 color = "black", 
                                 rot = 90, 
                                 size = 12,
                                 family = "serif"))
dev.off()

g4 <- pred_prob %>% 
  filter(origin_class %in% c(6, 7, 8, 9, 10) & destination_class %in% c(6, 7, 8, 9, 10)) %>%
  ggplot(., aes(x = monthyear, y = probs, group = origin_destination_class)) +
  geom_hline( yintercept = 0, linetype = "solid", colour = "gray85", size = 0.5) +
  geom_vline( xintercept = as.numeric(as.Date("2020-03-23")), linetype = "solid", colour = "gray85", size = 0.2) +
  geom_vline( xintercept = as.numeric(as.Date("2021-03-08")), linetype = "solid", colour = "gray85", size = 0.2) +
  geom_vline( xintercept = as.numeric(as.Date("2021-04-12")), linetype = "solid", colour = "gray85", size = 0.2) +
  geom_vline( xintercept = as.numeric(as.Date("2021-07-19")), linetype = "solid", colour = "gray85", size = 0.2) +
  geom_line(colour = "darkblue", size = 1) + 
  geom_ribbon(aes(ymin=(ci_lower), ymax=(ci_upper)), alpha=0.35, fill="gray36") +
  #facet_wrap(~ coefficient, nrow = 10) +
  facet_grid(origin_class ~ destination_class) +
  theme_tufte() +
  #theme(text = element_text(family="robotocondensed")) +
  theme(legend.position = "none",
        text=element_text(size=12),
        plot.subtitle = element_text(color = c('black'), hjust = 0.5, size = 12,face = "bold"),
        axis.text=element_text(size=8),
        axis.title=element_text(size=12)
  ) +
  labs(x= "Month",
       y = "Regression Probs",
       subtitle = "Destination Class") +
  scale_x_date(date_labels = "%b",
               date_breaks = "3 months", #breaks = c("Mar", "Jun", "Sep", "Dec"),
               limits = c(as.Date("2020-01-01"), as.Date("2021-08-01"))
  )

png("~/glm-probs_class_o6-10_d6-10.png",units="in", width=10, height=10, res=300)
annotate_figure(g4, 
                left = text_grob("Origin Class", 
                                 face= "bold", 
                                 color = "black", 
                                 rot = 90, 
                                 size = 12,
                                 family = "serif"))
dev.off()

```

